A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-05 Paper.tex
edits

\section{Beacon Initialization}
Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These methods are further  divided into delayed and undelayed initializations.
\subsection{Delayed/Offline initializations}
These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in[5 of Active range only beacon lov=calisationi],a posed based ekf as mentioned in[8] , a moving horizon estimation as mentioned in [9] etc. The most popular ones are mentioned below.

@@

In [SEIF PAER 1] they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition they factored in inter beacon measurements to reduce uncertainity even furthur. In [seif paper 2] it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.

>>>>

\section{Beacon Initialization}
Beacons initialization refers to the precursor process to the EKF where beacons (or landmarks) whose initial positions are not known are estimated. One of the complications with RO-SLAM involves the issue of the EKF, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These methods are further  divided into delayed and undelayed initializations.
\subsection{Delayed/Offline initializations}
These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman2003},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc. The most popular ones are mentioned below.

@@

In [SEIF PAER 1] they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition they factored in inter beacon measurements to reduce uncertainity even furthur. In \cite{Djugash2006} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
